Ripple Consensus Review

### 2015-04-26 paper.tex
Added attack flowchart and example

\section{Synergistic Attacks}

do a directed graph of likely synergistic attack sequences

>>>>

\section{Attack flowchart}

Figure \ref{fig:attack-flowchart} shows some of the stronger synergies between
different attacks.

Let's go through a full scenario, involving multiple attacks at once.  Ripple
Labs has diversified their default UNL such that the $80\%$ of the validators
are run by publicly known institutions evenly spread across the following five
countries, United States, France, Switzerland, Russia, and China, with the
remaining fifth being controlled by pseudoanonymous ``DarkWeb'' entities like
The Silk Road Five, and Agora Market. As any one entity only comprises at most
$1/6\text{th}$ of the UNL no single actor can block transactions.

The Russian government has issued a court order seizing assets of Royal Dutch
Shell, who has recently received funds from Naftogaz Ukraine to develop a new
fracking project. Naftogaz in turn owes Russia for unpaid natural gas imports -
quite a lot more than the funds Shell has, but simply punishing them for
working with Naftogaz is a good start.

By itself Russia is unable to freeze Shell's assets on the Ripple ledger
through coercion of Russian-jurisdiction validators. So Russia begins with a
transaction flood attack, slowly increasing load on the Ripple network to
$10\text{MB}/\text{sec}$ of transactions. As a cover story a new
gambling-oriented MMORPG is created that uses the Ripple ledger to record user
accounts; Ripple Labs is happy to sell them the XRP to cover transaction fees.

The transaction flood results in the pseudoanonymous ``DarkWeb'' validators
quitting - the Tor network is too slow to handle the load, and they worry
they're real identities will be discovered if they move their validator nodes
to clearnet hosting.

At this point Russia with $20\%$ UNL control could simply vote to freeze
Shell's assets, achieving a denial-of-service. However, it's decided it would
be better if the funds were actually recovered instead.

Russia sets up a fake Chinese oil importer, hiring another Chinese company to
do the actual transportation, and has them contact Shell asking to purchase
some oil. They also find a wealthy Chinese investor with \$100 million USD
worth of yuan in an account with a major Chinese bank, and has that investor
``invest'' in the new importer. Meanwhile Russia's cyberwarfare team gets to
work, succesfully compromising the Swiss and French validation nodes, and
using the fact that they have agents in major Ukrainian ISPs to sybil attack
the Ukrainian-based Shell office actually handling the sale. They can't
compromise the US nodes - they're on a newer version - but they do happen to
find a new zero-day consensus bug in the newer version.

On the day of the sale unknown to Shell their Ukrainian office's internet
connection is being filtered. The IT staff at their accounting office voices
concern when their Ripple node monitoring tools say that the US validators just
went off-line, although they're somewhat reassured when they hear news that the
US nodes just hit a consensus issue. The captain says there's bad weather
coming in, so they need to leave the port ASAP - with France and Switzerland
approving the transaction they have confidence that the Free World has approved
the money transfer.

What's actually happened is Russian cyberwarfare experts created a fake
consensus uses stolen Swiss and French private keys. Russia of course
officially signed this fake consensus, as well as the real consensus, taking
the position this was an above-the-board court ordered operation; China also
signed, but doesn't officially say why. The wealthy Chinese investor
conveniently claims to have suddenly found out about the ``fake'' oil importer
and on the real Ripple ledger has the funds frozen by the Chinese bank backing
them - not a big deal with the money still sitting in the original account he
deposited it too, still under Chinese jurisdiction.

Shell's Ukrainian office finally realises something is wrong after two hours of
debugging, trying to figure out why an exchange wasn't seeing their transaction
attempting to sell that yuan for USD. By that time the ship is in international
waters, and is happy to keep steaming to China, where upon the oil is kept for
the next ten years while the Chinese courts argue what to do with it.

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figures/attack-flowchart.eps}
    \caption{Attack flowchart}
    \label{fig:attack-flowchart}
\end{figure}
